Lightweight Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection

### 2016-09-21 paper/lncsFormat.tex
before update introduction

\begin{abstract}
Many web applications need the accurate event detection technique on microblog stream. 
But the accuracy of existing methods are still challenged by microblog's short length and high noise. 
We develop a novel lightweight transfer learning method \textsc{LTDetector} to deal with the task.  
\textsc{LTDetector} bases on two facts, that microblog is short but can be enriched by knowledge base semantically with transfer learning; and to make the transfer efficiently and effectively, the scale of knowledge should shrink without degrading. 
The following contributions are made in \textsc{LTDetector}.
(1) We formalize the knowledge base's hierarchical structure into three parts including taxonomy graph, category-page bipartite graph, and page-content map; and further shrink the scale of knowledge to category-word level.
The structure is utilized to condense category's highly related words and their chi-square scores, namely category's \textit{KB State}.
%The knowledge base's hierarchical structure is formalized as three-part: taxonomy graph, category-page bipartite graph, and page-content map.
%The structure is utilized to condense category's highly related words and their chi-square scores, namely category's \textit{KB State}, shrinking the scale of knowledge to category-word level.
(2) Category's related words in microblog stream, namely category's \textit{Stream State}, are learned from our proposed KB-Prior-LDA, which exploits the word co-occurrences and transfers the condensed knowledge \textit{KB State} into microblogs. 
(3) Events are further detected on meaningful categories' \textit{Stream States}, which filter out the noisy accurately. 
(4) Experiments on the benchmark \textit{Edinburgh twitter corpus (30 million tweets)} validate the effectiveness of our proposed transfer learning method.
\textsc{LTDetector} achieves high accuracy, promoting the precision by 9\% without  sacrificing the recall rate.

>>>>

\begin{abstract}
Many web applications need the accurate event detection technique on microblog stream. 
But the accuracy of existing methods are still challenged by microblog's short length and high noise. 
We develop a novel lightweight transfer learning method \textsc{LTDetector} to deal with the task.  
\textsc{LTDetector} bases on two facts, that microblog is short but can be enriched by knowledge base semantically with transfer learning; and to make the transfer efficiently and effectively, the scale of knowledge should shrink without degrading. 
The following contributions are made in \textsc{LTDetector}.
(1) We formalize the knowledge base's hierarchical structure into three parts including taxonomy graph, category-page bipartite graph, and page-content map; and further shrink the scale of knowledge to category-word level by utilizing the structure.
Specifically, category's highly related words and their chi-square scores, namely category's \textit{KB State}, are condensed.
%The knowledge base's hierarchical structure is formalized as three-part: taxonomy graph, category-page bipartite graph, and page-content map.
%The structure is utilized to condense category's highly related words and their chi-square scores, namely category's \textit{KB State}, shrinking the scale of knowledge to category-word level.
(2) Category's related words in microblog stream, namely category's \textit{Stream State}, are learned from our proposed KB-Prior-LDA, which exploits the word co-occurrences and transfers the condensed knowledge \textit{KB State} into microblogs. 
(3) Events are further detected on meaningful categories' \textit{Stream States}, which filter out the noise accurately. 
(4) Experiments on the benchmark \textit{Edinburgh twitter corpus (30 million tweets)} validate the effectiveness of our proposed transfer learning method.
\textsc{LTDetector} achieves high accuracy, promoting the precision by 9\% without  sacrificing the recall rate.
%另外，我们还标注了事件，使其语义可理解。以及LTDetector是efficient的。
